\mainmatter

# Introduction

Now unplug your Internet cable, and start doing some serious work.

We have a nice figure in Figure \@ref(fig:hello), and also a table in Table \@ref(tab:iris).

```{r hello, fig.cap='Hello World!', out.width='90%'}
par(mar = c(4, 4, 1, .1))
plot(cars, pch = 19)
```

```{r iris}
knitr::kable(
  head(iris), caption = 'The boring iris data.',
  booktabs = TRUE
)
```

More chapters to come in `02-foo.Rmd`, `03-bar`.Rmd, ...

## Hello bookdown

All chapters start with a first-level heading followed by your chapter title, like the line above. There should be only one first-level heading (`#`) per .Rmd file.

### A section

All chapter sections start with a second-level (`##`) or higher heading followed by your section title, like the sections above and below here. You can have as many as you want within a chapter.

### An unnumbered section {-}

Chapters and sections are numbered by default. To un-number a heading, add a `{.unnumbered}` or the shorter `{-}` at the end of the heading, like in this section.